\documentclass[12pt, a4paper]{article}

\usepackage[top=0.9in, bottom=0.8in, left=0.7in, right=0.8in]{geometry}
\usepackage{sectsty, enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage, hyperref}
\usepackage[parfill]{parskip}
\usepackage{bm}

\renewcommand{\headrulewidth}{0pt}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
    }
\usepackage[dvipsnames]{xcolor}

% set font style
\usepackage{helvet}
\usepackage[T1]{fontenc}

% set heading style
\usepackage{titlesec}
\titleformat{\section}{
  \vspace{-8pt}\bf\scshape\large\raggedright
}{}{0em}{}[\vspace{-6pt}]
% \titleformat{\section}{
%   \vspace{-4pt}\bfseries\large\raggedright\MakeUppercase
% }{}{1em}{}[\vspace{-5pt}]

% set spacing
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.15}

% set heaer and footer
\pagestyle{fancy}
\fancyhf{}
\fancypagestyle{firstpage}{
  \lhead{\textcolor{gray}{Last Updated on \today}}
}
\cfoot{\footnotesize{Page \thepage \hspace{1pt} of \pageref{LastPage}}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%----------------------------------------------------------------------------------------
%	Information
%----------------------------------------------------------------------------------------
\thispagestyle{firstpage}

{\par \centering\MakeUppercase{\Large\bf Guang Cheng} \par}
\vspace*{-2mm}
\centering
\footnotesize{National University of Singapore, Institute of Operations Research and Analytics} \\
\footnotesize{\#04-01, Innovation 4.0, 3 Research Link, Singapore 117602} \\
\footnotesize{\href{mailto:gcheng@u.nus.edu}{gcheng@u.nus.edu}} $\ \diamond \ $ \footnotesize{\href{https://gcheng-nus.github.io}{https://gcheng-nus.github.io}}



{\small
%----------------------------------------------------------------------------------------
%	Education SECTION
%----------------------------------------------------------------------------------------

\section*{Education}
\vspace*{0.4em}
\hrule height 0.4pt
 \begin{itemize}[leftmargin=20pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item[] \textbf{National University of Singapore, Singapore} \hfill \textit{2020 -- Present} \\
	\textit{Ph.D. Student in Operations Research and Analytics} \\
	Advisor: Joel Goh

	\item[] \textbf{University of Science and Technology of China, China} \hfill \textit{2016 -- 2021} \\
	\textit{Master in Management Science and Engineering} \\
	Advisors: Jingui Xie, Zhichao Zheng (external)

	\item[] \textbf{Jiangnan University, China} \hfill \textit{2012 -- 2016} \\
	\textit{Bachelor in Industrial Engineering}

\end{itemize}



%----------------------------------------------------------------------------------------
%	 Interest SECTION
%----------------------------------------------------------------------------------------

\section*{Research Interests}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=20pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item[] Medical Decision Making, Healthcare Operations Management, Scheduling Systems

\end{itemize}



%----------------------------------------------------------------------------------------
%	Paper SECTION
%----------------------------------------------------------------------------------------

\section*{Working Papers}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{enumerate}[leftmargin=36pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item Guang Cheng, Jingui Xie, Zhichao Zheng, Haidong Luo, Oon-Cheong Ooi.
	Extubation decision making with predictive information for mechanically ventilated patients in ICU.
	Major revision at {\it Management Science}.
	% (Previous title: Optimal stopping for medical treatment with forecast information)
	% [\href{https://ssrn.com/abstract=3397530}{{\color{Blue}\underline{SSRN}}}] 

\end{enumerate}



%----------------------------------------------------------------------------------------
%	Published Paper SECTION
%----------------------------------------------------------------------------------------

\section*{Published Paper}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{enumerate}[leftmargin=36pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item Guang Cheng, Sarah Yini Gao, Yancheng Yuan, Chenxiao Zhang, Zhichao Zheng. 
	On the test accuracy and effective control of the COVID-19 pandemic: A case study in Singapore. 
	{\it INFORMS Journal on Applied Analytics}, forthcoming.

	\item Jingui Xie, Guang Cheng, Zhichao Zheng, Haidong Luo, Oon-Cheong Ooi. To extubate or not to extubate: Risk factors for extubation failure and deterioration with further mechanical ventilation. {\it Journal of Cardiac Surgery}, 2019, 34(10): 1004–1011. %[\href{https://onlinelibrary.wiley.com/doi/abs/10.1111/jocs.14189}{{\color{Blue}\underline{Link}}}] 

\end{enumerate}



%----------------------------------------------------------------------------------------
%	Presentations SECTION
%----------------------------------------------------------------------------------------

\section*{Conference Presentations}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item Extubation decision making with predictive information for mechanically ventilated patients in ICU

	\begin{itemize}[leftmargin=20pt, itemsep=2pt, topsep=2pt]

		\item 2021, {\it The 13th International Conference of CSAMSE}, Shanghai, China (virtual)

		\item 2019, {\it POMS-HK International Conference}, Hong Kong, China

	\end{itemize}

\end{itemize}



%----------------------------------------------------------------------------------------
%	 Experience SECTION
%----------------------------------------------------------------------------------------

\section*{Professional Experience}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=4pt, parsep=0.2pt, topsep=1pt]

	\item {\it Research Assistant}: Singapore Management University, Jul. 2019 -- Jun. 2020

	\item {\it Research Assistant}: Singapore Management University, Aug. 2018 -- Nov. 2018

  \item {\it Research Assistant}: Singapore Management University, Sep. 2017 -- Mar. 2018

\end{itemize}



%----------------------------------------------------------------------------------------
%	 Experience SECTION
%----------------------------------------------------------------------------------------

\section*{Professional Service}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=5pt, parsep=0.2pt, topsep=1pt]

	\item {\it Organizing Committee Member}: Analytics for X Conference 2021

\end{itemize}



%----------------------------------------------------------------------------------------
%	Honors SECTION
%----------------------------------------------------------------------------------------

\section*{Honors and Awards}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=2pt, parsep=0.2pt, topsep=1pt]

	\item NUS Research Scholarship, National University of Singapore, Singapore, 2020
	
	\item JData Data Mining Competition Top 10, JD.com, inc., China, 2017

	\item National Scholarship, Ministry of Education of People’s Republic of China, China, 2015

	\item Municipal Merit Student, Education Bureau of Wuxi, China, 2015

\end{itemize}



%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------

\section*{Skills}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=2pt, parsep=0.2pt, topsep=1pt]

	\item {\it Programming \& Packages}: Python, R, MATLAB, SQL, Gurobi

\end{itemize}
}


% \vspace*{\fill}
% \center Last Updated on \today

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%