\documentclass[12pt, a4paper]{article}

\usepackage[top=0.7in, bottom=0.7in, left=0.7in, right=0.7in]{geometry}
% \usepackage{sectsty}
\usepackage{enumitem}
\usepackage{fancyhdr}
\setlength{\headheight}{15pt}
\usepackage{lastpage}
\usepackage[parfill]{parskip}
\setlength{\parskip}{1em}
\usepackage{bm}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
}
\usepackage[dvipsnames]{xcolor}

% set font style
\usepackage{helvet}
\usepackage[T1]{fontenc}

% set heading style
\usepackage{titlesec}
\titleformat{\section}{
  \vspace{-12pt}\scshape\Large\raggedright
}{}{0em}{}[\vspace{0pt}\hrule]

% set spacing
\renewcommand{\baselinestretch}{1.15}
\renewcommand{\headrulewidth}{0pt}
% set header and footer
\pagestyle{fancy}
\cfoot{\footnotesize{Page \thepage \hspace{1pt} of \hspace{1.5pt}\pageref{LastPage}}}

\usepackage{datetime}

\newdateformat{monthyeardate}{%
  \monthname[\THEMONTH] \THEYEAR}

\setlist[enumerate,1]{leftmargin=30pt, itemsep=0pt} % Enumerate Level 1
\setlist[enumerate,2]{itemsep=-2pt}   % Enumerate Level 2

\setlist[itemize,1]{leftmargin=16pt, itemsep=0pt}  % Level 1 (outermost)
\setlist[itemize,2]{itemsep=-4pt, label=$\bullet$}   % Level 2 (nested)
\setlist[itemize,3]{itemsep=-4pt, topsep=-4pt, label=$\circ$}   % Level 3 (deeply nested)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%----------------------------------------------------------------------------------------
%	Information
%----------------------------------------------------------------------------------------
% \thispagestyle{firstpage}

{\par \centering{\huge Guang CHENG} \par}
% \vspace*{-2mm}
\centering
{\footnotesize Institute of Operations Research and Analytics} \\
{\footnotesize National University of Singapore} \\
% \footnotesize{\#04-01, Innovation 4.0, 3 Research Link, Singapore 117602} \\
{\footnotesize \href{mailto:gcheng@u.nus.edu}{gcheng@u.nus.edu}} $\ \vert \ $ \footnotesize{\href{https://gcheng-nus.github.io}{https://gcheng-nus.github.io}} \\
\vspace*{0.5em}
{\footnotesize \textit{Last Updated in \monthyeardate\today}}

\vspace*{1em}

{\small
%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------

\section*{Education}

\begin{itemize}

	\item[]
	\textbf{National University of Singapore, Singapore} \hfill \textit{2020 -- Present} \\
	Ph.D. Candidate in Operations Research and Analytics \\
	Advisors: Joel Goh, S\i{}d\i{}ka Tun\c{c} Cando\u{g}an

	\item[]
	\textbf{University of Science and Technology of China, China} \hfill \textit{2016 -- 2019} \\
	M.S. in Management Science and Engineering

	\item[]
	\textbf{Jiangnan University, China} \hfill \textit{2012 -- 2016} \\
	B.S. in Industrial Engineering

\end{itemize}



%----------------------------------------------------------------------------------------
%	 Research Interests
%----------------------------------------------------------------------------------------

\section*{Research Interests}

\begin{itemize}
    \item[] \textbf{Topics:} Data-Driven Medical Decision-Making and Healthcare Operations; Behavioral Interventions in Healthcare  
    \item[] \textbf{Methodologies:} Econometric Analysis; Field Experiments; Data Analytics; Causal Inference
\end{itemize}



%----------------------------------------------------------------------------------------
%	Published Papers
%----------------------------------------------------------------------------------------

\section*{Published Work}

\begin{enumerate}

	\item Guang Cheng, Jingui Xie, Zhichao Zheng, Haidong Luo, Oon-Cheong Ooi.
	\href{https://doi.org/10.1287/mnsc.2021.01427}{Extubation Decisions with Predictive Information for Mechanically Ventilated Patients in the ICU.}
	\textit{\textbf{Management Science}}. Article in Advance.
	
	\item Stephanie Q. Ko, Guang Cheng, Tze Yeong Teng, Joel Goh.
	\href{https://doi.org/10.1016/j.jamda.2024.105154}{Home-First or Hospital-First? A Propensity Score-Weighted Retrospective Cohort Study.}
	\textit{\textbf{Journal of the American Medical Directors Association}}, 2024, 25(9):105154.
	
	\item Guang Cheng, Sarah Y. Gao, Yancheng Yuan, Chenxiao Zhang, Zhichao Zheng. 
	\href{https://doi.org/10.1287/inte.2022.1117}{On the Test Accuracy and Effective Control of the COVID-19 Pandemic: A Case Study in Singapore.} 
	\textit{\textbf{INFORMS Journal on Applied Analytics}}, 2022, 52(6):524-538.

	\item Jingui Xie, Guang Cheng, Zhichao Zheng, Haidong Luo, Oon-Cheong Ooi. 
	\href{https://doi.org/10.1111/jocs.14189}{To Extubate or Not to Extubate: Risk Factors for Extubation Failure and Deterioration with Further Mechanical Ventilation.}
	\textit{\textbf{Journal of Cardiac Surgery}}, 2019, 34(10): 1004–1011.

\end{enumerate}



%----------------------------------------------------------------------------------------
%	Working Paper
%----------------------------------------------------------------------------------------

\section*{Working Papers}

\begin{enumerate}[leftmargin=30pt, resume]
	
	\item Guang Cheng, S\i{}d\i{}ka Tun\c{c} Cando\u{g}an, Joel Goh, Bilal Gokpinar.
	\href{https://ssrn.com/abstract=4956298}{The Role of Contextual Information in Customer Reviews: A Field Experiment on a Mental Health Platform.} {\bf Major Revision} at \textit{\textbf{Management Science}}.

	\begin{itemize}
		\item {\footnotesize Finalist, 2025 POMS PITM Best Student Paper Competition}
		\item {\footnotesize Select for presentation at Workshop on Empirical Operations Management 2025}
	\end{itemize}

	\item Guang Cheng, Joshua M. Hagood, Ryan L. Melvin, Adam F. Kohutnicki, Mitchell H. Tsai, Joel Goh. The Impact of Introducing Release Times for Operating Rooms on Surgery Waiting Times.

\end{enumerate}



%----------------------------------------------------------------------------------------
%	Work in Progress
%----------------------------------------------------------------------------------------

% \section*{Work-in-Progress}

% \begin{enumerate}[leftmargin=30pt, resume]

% 	\item Incentive Design for Hospital at Home (with Joel Goh, Eryn J. He, Sergei Savin)
	
% 	\item Appointment Management in Outpatient Clinics (with Joel Goh and Hong Ming Tan)
	
% 	\item Retain Clients on Mental Health Platform (with S\i{}d\i{}ka Tun\c{c} Cando\u{g}an and Yueyang Zhong) 
	
% \end{enumerate}



%----------------------------------------------------------------------------------------
%	 Teaching
%----------------------------------------------------------------------------------------

\section*{Teaching Experience}
% \begingroup
% \setstretch{1.0}
\begin{itemize}

	\item[] \textbf{Instructor}
	\begin{itemize}
		\item DAO1704 Decision Analytics using Spreadsheets (BBA) \hfill Spring 2023
		\begin{itemize}
			% \item {\footnotesize Class size: 35 students}
			% \item {\footnotesize Delivered core analytics course for business undergraduates, integrating real-world healthcare and business applications.}
			\item {\footnotesize Teaching evaluation: 4.2/5 (department average: 4.0)}
			\item {\footnotesize Teaching Excellence Award for Graduate Instructor}
		\end{itemize}
	\end{itemize}

	\item[] \textbf{Guest Lecturer}
	\begin{itemize}
		\item DBA4811 Analytics for Consulting (BBA) \hfill Spring 2025
		\begin{itemize}
			\item {\footnotesize Conducted two lectures on machine learning techniques and their applications.}
		\end{itemize}
		\item PHM5014 Causal Inference in Precision Medicine (MScPHM) \hfill Fall 2024
		\begin{itemize}
			\item {\footnotesize Presented the Safe Space experiment to illustrate real-world applications of causal inference, demonstrating how empirical methods inform policy and operational decisions in real business.}
		\end{itemize}
	\end{itemize}

	\item[] \textbf{Teaching Assistant}
	\begin{itemize}
		\item DBA4811 Analytics for Consulting (BBA) \hfill Spring 2025
		\item DBA5103 Operations Research and Analytics (MSBA) \hfill Fall 2022
		\item IE4214 Revenue Management and Pricing Analytics (BEng) \hfill Spring 2022
	\end{itemize}
\end{itemize}
% \endgroup


%----------------------------------------------------------------------------------------
%	Presentations
%----------------------------------------------------------------------------------------

\section*{Conference Presentations}

\begin{itemize}

	\item[] {\it The Role of Contextual Information in Customer Reviews: A Field Experiment on a Mental Health Platform}
	\begin{itemize}
		\item POMS Annual Conference, Atlanta, Georgia, USA (scheduled) \hfill May 2025
		\item Workshop on Empirical Operations Management, Hong Kong, China \hfill Jan 2025
		\item The 15th POMS-HK International Conference, Hong Kong, China \hfill Jan 2025
		\item INFORMS Annual Meeting, Seattle, Washington, USA \hfill Oct 2024
		\item The 16th International Annual Conference of CSAMSE, Xiamen, China \hfill Jul 2024
	\end{itemize}

	\item[] {\it The Impact of Introducing Release Policy for Operating Rooms on Surgery Waiting Times}
	\begin{itemize}
		\item INFORMS Annual Meeting, Phoenix, Arizona, USA \hfill Oct 2023
		\item POMS Annual Conference, Orlando, Florida, USA \hfill May 2023
		\item The 13th POMS-HK International Conference, Hong Kong, China \hfill Jan 2023
		\item INFORMS Annual Meeting, Indianapolis, Indiana, USA \hfill Oct 2022
		\item POMS Annual Conference, Orlando, Florida, USA (Online) \hfill Apr 2022
		% \item IARS Annual Meeting, poster presentation, virtual \hfill Mar 2022
	\end{itemize}

	\item[] {\it Extubation Decisions with Predictive Information for Mechanically Ventilated Patients in ICU}
	\begin{itemize}
		\item POMS Annual Conference, Orlando, Florida, USA (Online) \hfill Apr 2022
		\item The 13th International Annual Conference of CSAMSE, Shanghai, China (Online) \hfill Jul 2021
		\item The 10th POMS-HK International Conference, Hong Kong, China \hfill Jan 2019
	\end{itemize}

\end{itemize}



%----------------------------------------------------------------------------------------
%	 Experience
%----------------------------------------------------------------------------------------

\section*{Professional Experience}

\begin{itemize}[leftmargin=30pt]
    \item Visiting Scholar, Virginia Tech, Blacksburg, Virginia, USA, Aug 2023 -- Dec 2023	
    \item Research Assistant, Singapore Management University, Singapore, Jul 2019 -- Jun 2020
	% \item Visiting Student, Singapore Management University, Singapore, Aug 2018 -- Nov 2018
    % \item Visiting Student, Singapore Management University, Singapore, Sept 2017 -- Mar 2018
\end{itemize}



%----------------------------------------------------------------------------------------
%	 Service
%----------------------------------------------------------------------------------------

\section*{Services and Activities}

\begin{itemize}

	\item[] \textbf{Journal Reviewer}
	\begin{itemize}
		\item Humanities and Social Sciences Communications
	\end{itemize}

	\item[] \textbf{Conference Reviewer}
	\begin{itemize}
		\item MSOM 2025
	\end{itemize}

	\item[] \textbf{Conference Session Chair}
	\begin{itemize}
		\item INFORMS Annual Meeting \hfill Oct 2025
		\item INFORMS International Meeting \hfill Jul 2025
		\item POMS-HK International Conference \hfill Jan 2025
		\item POMS Annual Conference \hfill May 2023
		% \item INFORMS Annual Meeting \hfill Sept 2022
		\item Analytics for X Conference \hfill Sept 2022
		\item POMS Annual Conference \hfill Apr 2022
	\end{itemize}

	\item[] \textbf{Organizing Committee}
	\begin{itemize}
		\item Analytics for X Conference \hfill Sept 2021
	\end{itemize}

	% \item[] \textbf{Professional Memberships}
	% \begin{itemize}[label=$\bullet$]
	% 	\item Institute for Operations Research and Management Sciences (INFORMS)
	% 	\item INFORMS Health Applications Society (HAS)
	% \end{itemize}

\end{itemize}



%----------------------------------------------------------------------------------------
%	Honors
%----------------------------------------------------------------------------------------

\section*{Honors and Awards}

\begin{itemize}[leftmargin=30pt]
	\item Finalist, POMS PITM Best Student Paper Competition \hfill 2025
	\item Teaching Excellence Award for Graduate Instructor \hfill 2023
	\item NUS Research Scholarship, National University of Singapore \hfill 2020--2024
	\item JData Data Mining Competition Top 10, JD.com, inc. \hfill 2017
	\item National Scholarship, Ministry of Education of People's Republic of China \hfill 2015
\end{itemize}



%----------------------------------------------------------------------------------------
%	Skills
%----------------------------------------------------------------------------------------

\section*{Skills}

\begin{itemize}
	\item[] \textbf{Programming \& Packages}: Python, R, MATLAB, SQL, Gurobi
	\item[] \textbf{Languages}: English (Fluent), Mandarin (Native)
\end{itemize}


}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%